\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
so far
lol

Considering the number of articles that passed the screening phase

For the classification phase, we distributed the 94 articles evenly among the
three evaluators.
Each article has been read thoroughly and classified according to the
classification scheme if considered relevant to the study.

Misleading articles that passed screening phase were removed at that point.
A total of 39 articles have been rejected in this fashion.

@@

@@

@@

\subsection{Publication Venue Distribution}
% Need a graphic for article by publishers.

\subsection{Publication type distribution}
\begin{figure}
  \centering
  \includegraphics[scale=0.40]{doctype.png}
  \caption{Distribution of papers by type of document}
\end{figure}

% Need a graphic for article by publishers.

@@

Of interest is the relation between the type of analysis and the type of
patterns detected. \textit{Fig. 5} and \textit{Fig. 6}
respectively presents the distribution of the number of articles and their
proportion in this relation.

>>>>

For the classification phase, we distributed the 94 articles evenly among the
three evaluators.
Each article has been read thoroughly and classified according to the
classification scheme by individual reviewers if considered relevant to the
study.

Misleading articles that passed screening phase were removed at that point.
A total of 39 articles have been rejected in this fashion leaving a total of
55 articles relevant to our study

The resulting classification and interpretation will be discussed in the next
section.

@@

In this section, the article will analyse different measures obtained from
the final set of articles.
More precisely, the article will look at the yearly distribution, the publisher
distribution, the publication type distribution and each category define
earlier in the classification scheme.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.40]{publisher.png}
  \caption{Distribution of papers by publishers}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.40]{doctype.png}
  \caption{Distribution of papers by type of document}
\end{figure}

@@

\subsection{Publishers Distribution}

\textit{Fig. 4} shows a partial distribution of the articles between their
resspective publishers. 
In many cases, data exported from Scopus is lacking the publisher which
resulted in the classification of many articles as \textit{Other}.
Manual inspection would be required.

\subsection{Publication type distribution}

\textit{Fig. 5} shows the distribution of the papers according to their
types.
Unsurprisingly, half of them are conference paper, while a third are journal
articles.

@@

Of interest is the relation between the type of analysis and the type of
patterns detected. \textit{Fig. 7} and \textit{Fig. 8}
respectively presents the distribution of the number of articles and their
proportion in this relation.
